Ice sheet mass flows

### 2024-06-05 sankey.tex
refactor internal variable and node names.

    \sankeyset{
      def data/.code args={#1/#2/#3}{% node name/label/values
        \LabSet{#1}{#2}
        \QSet{#1}{#3}
        \typeout{#1: \Q{#1} Gt (\Lab{#1})}
      },
      def data/.list={
        %% INSERT_CSV_HERE
        %% COMPUTED 
        {ML/Mass loss/
          (\Q{SU}+\Q{RU}+\Q{BM}+\Q{DYN}+\Q{FRET}+\Q{GZRET}+\Q{EV})-
          (\Q{SF}+\Q{RF}+\Q{CD}+\Q{DP})},
        {MLfd/Mass Loss fixed domain/\Q{ML}-(\Q{FRET}+\Q{GZRET})},
        {MG/Mass gain/
          (\Q{SF}+\Q{RF}+\Q{CD}+\Q{DP})-
          (\Q{SU}+\Q{RU}+\Q{BM}+\Q{DYN}+\Q{FRET}+\Q{GZRET}+\Q{EV})}
      },
    }

@@

    \sankeynode{name=SF, quantity=\Q{SF}}
    \sankeynode{name=DP, quantity=\Q{DP}, at={[xshift=-\xoff]SF.right}, anchor=left}
    \sankeynode{name=CD, quantity=\Q{CD}, at={[xshift=-\xoff]DP.right}, anchor=left}
    \sankeynode{name=RF, quantity=\Q{RF}, at={[xshift=-\xoff]CD.right}, anchor=left}

@@

    \sankeynode{name=f0, quantity=\Q{SF}+\Q{DP}+\Q{CD}+\Q{RF},
      at={[yshift=-15mm]SF.left}, anchor=left,
      forked={\Q{SF}/SF-in, \Q{DP}/DP-in, \Q{CD}/CD-in, \Q{RF}/RF-in}}

    \sankeyoutin{SF}{SF-in}
    \sankeydubins[minimum radius=3mm,air-to-ice]{DP}{DP-in}
    \sankeydubins[minimum radius=3mm]{CD}{CD-in}
    \sankeydubins[minimum radius=3mm,water-to-ice]{RF}{RF-in}

    \ifthenelse{\Q{MG} > \Q{ML}}
    {
      \sankeynode{name=f1, quantity=\Q{RFZ}+\qq{f0},
        at={[yshift=-15mm,xshift=-3mm]f0.right}, anchor=right,
        forked={\qq{f0}/f0-in, \Q{RFZ}/RFZ-in}}
    }
    {
      \sankeynode{name=f1, quantity=\Q{RFZ}+\qq{f0}+\Q{ML},
        at={[yshift=-15mm]f0.center}, anchor=center,
        forked={\Q{ML}/ML-in, \qq{f0}/f0-in, \Q{RFZ}/RFZ-in}}
    }

    \sankeyoutin{f0}{f0-in}
    \sankeyadvance{f1}{15mm}

    \ifthenelse{\Q{MG} > \Q{ML}}
    {
      \sankeyfork{f1}{
        \Q{MG}/fMG,
        \Q{SU}/fSU, \Q{FRET}/fFR, \Q{GZRET}/fGZ,
        \Q{DYN}/f6, \Q{BM}/fBM, \Q{RU}+\Q{EV}/f8, \Q{RFZ}/RFZ-out}
    }
    {
      \sankeyfork{f1}{
        %% \Q{MG}/fMG,
        \Q{SU}/fSU, \Q{FRET}/fFR, \Q{GZRET}/fGZ,
        \Q{DYN}/f6, \Q{BM}/fBM, \Q{RU}+\Q{EV}/f8, \Q{RFZ}/RFZ-out}
    }

    \sankeydubins[minimum radius=5mm,ice-to-water-horiz]{RFZ-out}{RFZ-in}

    \sankeyadvance{f6}{10mm}
    \sankeyfork{f6}{\Q{ICE}/fD, \Q{SUB}/fSUB}
    \sankeyadvance{fD}{10mm}

    \sankeynode{name=fSUBa, quantity=\qq{fSUB},
      at={[xshift=-\xoff]fD.right}, anchor=left}
    \sankeyoutin[ice-to-water]{fSUB}{fSUBa}

    \sankeynode{name=fBMa, quantity=\qq{fBM},
      at={[xshift=-\xoff]fSUBa.right}, anchor=left}
    \sankeyoutin[ice-to-water]{fBM}{fBMa}

    \sankeynode{name=f8a, quantity=\qq{f8},
      at={[xshift=-\xoff]fBMa.right}, anchor=left}
    \sankeyoutin[ice-to-water]{f8}{f8a}

    \sankeynode{name=fGZa, quantity=\qq{fGZ},
      at={[xshift=\xoff]fD.left}, anchor=right}
    \sankeyoutin{fGZ}{fGZa}

    \sankeynode{name=fFRa, quantity=\qq{fFR},
      at={[xshift=\xoff]fGZa.left}, anchor=right}
    \sankeyoutin{fFR}{fFRa}

    \sankeynode{name=fSUa, quantity=\qq{fSU},
      at={[xshift=\xoff]fFRa.left}, anchor=right}
    \sankeyoutin{fSU}{fSUa}

    \ifnum \numexpr\Q{MG} > \Q{ML}
      \sankeynode{name=fMGa, quantity=\qq{fMG},
        at={[xshift=\xoff,yshift=8mm]fSUa.left}, anchor=right, angle=0}
      \sankeyoutin{fMG}{fMGa}
    \fi

    \sankeyfork{f8a}{\Q{RU}/fRU, \Q{EV}/fEV}
    \sankeynode{name=fEVa, quantity=\qq{fEV},
      at={[xshift=-3mm,yshift=-5mm]f8a.right}, anchor=right, angle=180}
    \sankeyoutin[water]{fEV}{fEVa}
    \sankeyadvance[water-to-air-horiz]{fEVa}{5mm}
    \sankeyend[air]{fEVa}

    \ifthenelse{\Q{MG} < \Q{ML}}
      {
        %% mass loss
        \sankeynode{name=fML, quantity=\Q{ML}, at={[xshift=\xoff,yshift=0mm]SF.left}, anchor=right}%, angle=-145}
        \sankeystart[red]{fML}
        \sankeyadvance[red-to-ice]{fML}{5mm}
        \sankeyoutin{fML}{ML-in}
      }
      {
        %% mass gain
        \sankeyadvance[ice-to-black]{fMGa}{3mm}
        \sankeyend[black]{fMGa}
      }

      \sankeynode{name=fSUa2, quantity=\qq{fSU},
        at={[xshift=2mm,yshift=-5mm]fSUa.left}, anchor=left, angle=0}
      \sankeyoutin[ice]{fSUa}{fSUa2}
      \sankeyadvance[ice-to-air-horiz]{fSUa2}{2mm}
      \sankeyend[air]{fSUa2}

      \sankeyadvance[out-red]{fFRa}{10mm}
      \sankeyend[out-red]{fFRa}
      \sankeyadvance[ice-to-water,out-red]{fGZa}{10mm}
      \sankeyend[water,out-red]{fGZa}
      \sankeyadvance{fD}{10mm}
      \sankeyend{fD}

      \sankeyset{water}
      \sankeyadvance{fBMa}{10mm}; \sankeyend{fBMa}
      \sankeyadvance{fSUBa}{10mm}; \sankeyend{fSUBa}
      \sankeyadvance{fRU}{10mm}; \sankeyend{fRU}

  %%   %% DRIFT
  %%   \sankeynode{name=DRIFT-OUT, quantity=33, at={(3mm, -8mm)}, angle=150}
  %%   \sankeynode{name=DRIFT-IN, quantity=33, at={(-3mm, -8mm)}, angle=210}
  %%   \sankeydubins[minimum radius=5mm]{DRIFT-OUT}{DRIFT-IN}
  %%   \sankeystart{DRIFT-OUT}
  %%   \sankeyend{DRIFT-IN}
  %%   \node[anchor=center, align=center, rotate=0, shift=({0,0})] at (0,-15mm) {Drifting (?)};

>>>>

    \sankeyset{
      def data/.code args={#1/#2/#3}{% node name/label/values
        \LabSet{#1}{#2}
        \QSet{#1}{#3}
        \typeout{#1: \Q{#1} Gt (\Lab{#1})}
      },
      def data/.list={
        %% INSERT_CSV_HERE
        %% COMPUTED 
        {vML/Mass loss/
          (\Q{vSU}+\Q{vRU}+\Q{vBM}+\Q{vDYN}+\Q{vFRET}+\Q{vGZRET}+\Q{vEV})-
          (\Q{vSF}+\Q{vRF}+\Q{vCD}+\Q{vDP})},
        {vMLfd/Mass Loss fixed domain/\Q{vML}-(\Q{vFRET}+\Q{vGZRET})},
        {vMG/Mass gain/
          (\Q{vSF}+\Q{vRF}+\Q{vCD}+\Q{vDP})-
          (\Q{vSU}+\Q{vRU}+\Q{vBM}+\Q{vDYN}+\Q{vFRET}+\Q{vGZRET}+\Q{vEV})}
      },
    }

@@

    \sankeynode{name=SF, quantity=\Q{vSF}}
    \sankeynode{name=DP, quantity=\Q{vDP}, at={[xshift=-\xoff]SF.right}, anchor=left}
    \sankeynode{name=CD, quantity=\Q{vCD}, at={[xshift=-\xoff]DP.right}, anchor=left}
    \sankeynode{name=RF, quantity=\Q{vRF}, at={[xshift=-\xoff]CD.right}, anchor=left}

@@

    \sankeynode{name=f0, quantity=\Q{vSF}+\Q{vDP}+\Q{vCD}+\Q{vRF},
      at={[yshift=-15mm]SF.left}, anchor=left,
      forked={\Q{vSF}/SFi, \Q{vDP}/DPi, \Q{vCD}/CDi, \Q{vRF}/RFi}}

    \sankeyoutin{SF}{SFi}
    \sankeydubins[minimum radius=3mm,air-to-ice]{DP}{DPi}
    \sankeydubins[minimum radius=3mm]{CD}{CDi}
    \sankeydubins[minimum radius=3mm,water-to-ice]{RF}{RFi}

    \ifthenelse{\Q{vMG} > \Q{vML}}
    { % mass gain
      \sankeynode{name=f1, quantity=\Q{vRFZ}+\qq{f0},
        at={[yshift=-15mm]f0.left}, anchor=left,
        forked={\qq{f0}/f0i, \Q{vRFZ}/RFZi}}
    }
    { % mass loss
      \sankeynode{name=f1, quantity=\Q{vRFZ}+\qq{f0}+\Q{vML},
        at={[yshift=-15mm]f0.left}, anchor=left,
        forked={\qq{f0}/f0i, \Q{vML}/MLi, \Q{vRFZ}/RFZi}}
    }

    \sankeyoutin{f0}{f0i}
    \sankeyadvance{f1}{15mm}

    \ifthenelse{\Q{vMG} > \Q{vML}}
    {
      \sankeyfork{f1}{
        \Q{vMG}/MG,
        \Q{vSU}/SU, \Q{vFRET}/FR, \Q{vGZRET}/GZ,
        \Q{vDYN}/f6, \Q{vBM}/BM, \Q{vRU}+\Q{vEV}/f8, \Q{vRFZ}/RFZo}
    }
    {
      \sankeyfork{f1}{
        %% \Q{vMG}/MG,
        \Q{vSU}/SU, \Q{vFRET}/FR, \Q{vGZRET}/GZ,
        \Q{vDYN}/f6, \Q{vBM}/BM, \Q{vRU}+\Q{vEV}/f8, \Q{vRFZ}/RFZo}
    }

    \sankeydubins[minimum radius=5mm,ice-to-water-horiz]{RFZo}{RFZi}

    \sankeyadvance{f6}{10mm}
    \sankeyfork{f6}{\Q{vICE}/D, \Q{vSUB}/SUB}
    \sankeyadvance{D}{10mm}

    \sankeynode{name=SUBa, quantity=\qq{SUB},
      at={[xshift=-\xoff]D.right}, anchor=left}
    \sankeyoutin[ice-to-water]{SUB}{SUBa}

    \sankeynode{name=BMa, quantity=\qq{BM},
      at={[xshift=-\xoff]SUBa.right}, anchor=left}
    \sankeyoutin[ice-to-water]{BM}{BMa}

    \sankeynode{name=f8a, quantity=\qq{f8},
      at={[xshift=-\xoff]BMa.right}, anchor=left}
    \sankeyoutin[ice-to-water]{f8}{f8a}

    \sankeynode{name=GZa, quantity=\qq{GZ},
      at={[xshift=\xoff]D.left}, anchor=right}
    \sankeyoutin{GZ}{GZa}

    \sankeynode{name=FRa, quantity=\qq{FR},
      at={[xshift=\xoff]GZa.left}, anchor=right}
    \sankeyoutin{FR}{FRa}

    \sankeynode{name=SUa, quantity=\qq{SU},
      at={[xshift=\xoff]FRa.left}, anchor=right}
    \sankeyoutin{SU}{SUa}

    \ifnum \numexpr\Q{vMG} > \Q{vML}
      \sankeynode{name=MGa, quantity=\qq{MG},
        at={[xshift=\xoff,yshift=8mm]SUa.left}, anchor=right, angle=0}
      \sankeyoutin{MG}{MGa}
    \fi

    \sankeyfork{f8a}{\Q{vRU}/RU, \Q{vEV}/EV}
    \sankeynode{name=EVa, quantity=\qq{EV},
      at={[xshift=-3mm,yshift=-5mm]f8a.right}, anchor=right, angle=180}
    \sankeyoutin[water]{EV}{EVa}
    \sankeyadvance[water-to-air-horiz]{EVa}{5mm}
    \sankeyend[air]{EVa}

    \ifthenelse{\Q{vMG} < \Q{vML}}
      {
        %% mass loss
        \sankeynode{name=ML, quantity=\Q{vML},
          at={[xshift=-\xoff]RF.right}, anchor=left} %, angle=-45}
        \sankeystart[red]{ML}
        \sankeyadvance[red-to-ice]{ML}{5mm}
        \sankeyoutin{ML}{MLi}
      }
      {
        %% mass gain
        \sankeyadvance[ice-to-black]{MGa}{3mm}
        \sankeyend[black]{MGa}
      }

      \sankeynode{name=SUaa, quantity=\qq{SU},
        at={[xshift=2mm,yshift=-5mm]SUa.left}, anchor=left, angle=0}
      \sankeyoutin[ice]{SUa}{SUaa}
      \sankeyadvance[ice-to-air-horiz]{SUaa}{2mm}
      \sankeyend[air]{SUaa}

      \sankeyadvance[out-red]{FRa}{10mm}
      \sankeyend[out-red]{FRa}
      \sankeyadvance[ice-to-water,out-red]{GZa}{10mm}
      \sankeyend[water,out-red]{GZa}
      \sankeyadvance{D}{10mm}
      \sankeyend{D}

      \sankeyset{water}
      \sankeyadvance{BMa}{10mm}; \sankeyend{BMa}
      \sankeyadvance{SUBa}{10mm}; \sankeyend{SUBa}
      \sankeyadvance{RU}{10mm}; \sankeyend{RU}

  %%   %% DRIFT
  %%   \sankeynode{name=DRIFTo, quantity=33, at={(3mm, -8mm)}, angle=150}
  %%   \sankeynode{name=DRIFTi, quantity=33, at={(-3mm, -8mm)}, angle=210}
  %%   \sankeydubins[minimum radius=5mm]{DRIFTo}{DRIFTi}
  %%   \sankeystart{DRIFTo}
  %%   \sankeyend{DRIFTI}
  %%   \node[anchor=center, align=center, rotate=0, shift=({0,0})] at (0,-15mm) {Drifting (?)};
